The Ranked Nearest Neighbour Interchange space

### 2019-07-01 paper.tex
edit beginning of section diameter

Following the results of section~\ref{section:caterpillar_convex} one can directly improve this result by giving the exact diameter of the $\rnni$ graph.

\begin{lemma}
	There are two caterpillar trees in $\rnniu$ with distance $\frac{(n-1)(n-2))}{2}$.
	\label{conj:caterpillar_diameter}
\end{lemma}

\todo{This is already an implication of the results above. Shall we still keep a subsection for Diameter? In case we find something about the radius, this could be added here.}

>>>>

With the results of Section~\ref{section:caterpillar_convex} we can easily provide the exact diameter of the $\rnni$ graph and hence, improve the bounds for the diameter given in \autocite{Gavryushkin2017}.
Moreover, we can conclude from Lemma~\ref{lemma:caterpillar_diameter} that the maximum distance computed by Algorithm~\ref{alg:find_path} equals the diameter of $\rnni$.
This quality of the algorithm suggests that it gives reasonable estimates of distances.
For further details on the quality of that algorithm we refer the reader to Section~\ref{section:computation}.

\begin{lemma}
	There are two caterpillar trees in $\rnniu$ with distance $\frac{(n-1)(n-2))}{2}$.
	\label{lemma:caterpillar_diameter}
\end{lemma}
